Stack Safety as Security Property

### 2020-05-28 props.tex
Some comments for Sean

@@

    Our properties are defined in terms of observations, which may be silent or a word of data:
    \[\obs \in \OBSS = \tau | \word \in \WORDS\]

    Execution is by a step function \(\mach \stepstoobs{\obs} \mach' : \MACHS \rightarrow
    \OBSS \times \MACHS\).

    A policy is a general model of an enforcement mechanism, consisting of
    a set of policy states, \(\pol \in \POLS\), a policy initializer
    \(pinit : \MACHS \rightharpoonup \POLS\), and a policy step function \(\pol \stepstopol \pol' :
    \POLS \rightharpoonup \POLS\). The initializer and step function are both partial functions,
    the former to reflect static guarantees (some initial states may not be valid at all) and
    the latter to reflect dynamic fail-stop behavior. We then define machine-policy pairs and
    a step function on them:

@@

    We identify infinite traces with \(\isinf(T\). We define a ``trace-of'' operator \(\hookrightarrow\)
    that coinductively relates a machine state with the trace of machine states paired with observations
    produced by repeated application of step:

@@

    [Coq difference alert: this operation steps until it reaches a state on which \(f\) holds,
    and is infinite if it doesn't. It doesn't compute the observation of the step after the final,
    which coq would. So coq may need a ``step until'' relation rather than ``prefix up to''.
    Still thinking about this.]

@@

    \[\frac{\obsT_1 = w \obsT_1' \hspace{.5cm} \obsT_2 = w \obsT_2'}
           {\obsT_1 \lesssim \obsT_2}\]

    [This is the same as the coq version minus a redundant case.]

@@

    [Coq difference alert: this should be equivalent to the coq version, and we should adopt it.]

@@

    [Todo: update coq to use this.]

@@

    [Coq difference alert: safe initialization is implemented differently in each property, since
     it's really just confidentiality. But because there's no return it's functionally the same.]

@@

>>>>

  \leo{Low level presentation point that slightly bugs me: }

@@

    Our properties are defined in terms of observations, which may be silent or a word of data:
    \[\obs \in \OBSS = \tau ~ | ~ \word \in \WORDS\]

    Execution is by\leo{is by?} a step function \(\mach \stepstoobs{\obs} \mach' : \MACHS \rightarrow
    \OBSS \times \MACHS\).

    A policy is a general model of an enforcement mechanism, consisting of
    a set of policy states, \(\pol \in \POLS\), a policy initializer
    \(\pinit : \MACHS \rightharpoonup \POLS\), and a policy step function \(\pol \stepstopol \pol' :
    \POLS \rightharpoonup \POLS\). The initializer and step function are both partial functions,
    the former to reflect static guarantees (some initial states may not be valid at all) and
    the latter to reflect dynamic fail-stop behavior. We then define machine-policy pairs and
    a step function on them:

@@

    We identify infinite traces with \(\isinf(T)\). We define a ``trace-of'' operator \(\hookrightarrow\)
    that coinductively relates a machine state with the trace of machine states paired with observations
    produced by repeated application of step:

@@

    \COQ{this operation steps until it reaches a state on which \(f\) holds,
    and is infinite if it doesn't. It doesn't compute the observation of the step after the final,
    which coq would. So coq may need a ``step until'' relation rather than ``prefix up to''.
    Still thinking about this.}\leo{So this is strictly weaker than the one we have in Coq, right?
      So its only the Eager implies Lazy direction that might need tweaking, but not the Test implies Eager one?}
    \leo{Also, it steps until it reaches an f-state or if the policy raises a fault}

@@

    \[\frac{\obsT_1 = w \obsT_1' \hspace{.5cm} \obsT_2 = w \obsT_2'}
           {\obsT_1 \lesssim \obsT_2}\]
    \leo{Doesn't this case miss the recursive $\obsT_1 \lesssim \obsT_2$ condition?}

    \COQ{This is the same as the coq version minus a redundant case.}

@@

    \COQ{this should be equivalent to the coq version, and we should adopt it.}
    \leo{We had this, but it was much harder to work with for my proofs. We should still
      prove them equivalent if we want to present it this way (which is probably cleaner for
      presentation purposes)}

@@

    [Todo: update coq to use this.]
    \leo{Oh, I like this version. Should make things cleaner in the top part of my proofs
      while leaving the hard low-level invariants unaffected.}

@@

    \COQ{safe initialization is implemented differently in each property, since
     it's really just confidentiality. But because there's no return it's functionally the same.}

@@

    \leo{Do we really need safe initialization? Couldn't we just use the definitions of
      integrity and confidentiality for the toplevel, pointing out that since it never
      returns only confidentiality is interesting? Or would we miss something?}
